Carbonate chemistry at Ny-Ålesund

### 2022-04-07 awipev-CO2.Rmd
changed plot at vs s

```{r Discrete salinity vs TA, echo=FALSE, fig.align="center", message=FALSE, warning=FALSE, out.width="100%"}
d_all_at_discrete <- d_all %>% #  To remove an outlier in red
  dplyr::select(datetime, monthd,closest_datetime, at, sal_fb_mix)
reg <- ggreg(
  xdata = d_all$sal_fb_mix,
  ydata = d_all$at,
  type = "OLS",
  plot = TRUE,
  title = "Discrete total alkalinity vs salinity",
  #subtitle = "",
  xlab = "Salinity",
  ylab = TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"),
  proplot = TRUE,
  #ylim(c(30.5,35.5)) + xlim(c(28,35.5)),
  coord_fixed(ratio = 1)
)
print(reg$plot)
ggsave(filename = "figures/at_s.png", plot = reg$plot, width = 25, height = 20, units = "cm")

@@

The relationship between titrated total alkalinity (references) and
salinity is very good with an r2 of
`r #round(summary(fit)$r.squared, digits=2)`. Need to compare with other
relationships from the literature.

>>>>

```{r Discrete salinity vs TA, echo=FALSE, fig.align="center", message=FALSE, warning=FALSE, out.width="100%"}
d_all_at_discrete <- d_all %>% #  To remove an outlier in red
  dplyr::select(datetime, monthd, closest_datetime, at, sal_fb_mix)
reg <- ggreg(
  xdata = d_all$sal_fb_mix,
  ydata = d_all$at,
  type = "OLS",
  plot = TRUE,
  title = "Discrete total alkalinity vs salinity",
  #subtitle = "",
  xlab = "Salinity",
  ylab = TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"),
  proplot = TRUE,
  #ylim(c(30.5,35.5)) + xlim(c(28,35.5)),
  coord_fixed(ratio = 1)
)
print(reg$plot)
ggsave(filename = "figures/at_s.png", plot = reg$plot, width = 25, height = 20, units = "cm")

@@

The relationship between titrated total alkalinity (references) and
salinity is very good with an r2 of
`r round(reg$fit$rsquare, digits = 2)`. Need to compare with other relationships from the literature.
